What covert verbal actions tell us about the interplay between language, action, and perception

### 2021-05-17 manuscript.tex
minor updates to intro

% Succinct introduction in four paragraphs.
% 1) Introduction of motor imagery
% 2) Covert verbals actions
% 3) Relating 1) and 2) to the thematic of the research topic
% 4) Aims of the present perspective

The ability to mentally examine our thoughts is central to our subjective experience. Mentally anticipating or rehearsing (verbal) actions allows us to become better at performing them (citation), to explore novel situations (citation), or to (citation)... Broadly construed, motor imagery can be defined as the mental process by which one rehearses an action without engaging in the physical movements involved in this particular action. Because speech production results from sequences of motor commands which are assembled to reach a given communication goal, it belongs to the broader category of motor actions \citep{jeannerod_motor_2006}. Therefore, a parallel can be drawn between covert speech (also known as \textit{inner speech} or \textit{speech imagery}) and other forms of covert verbal actions (e.g., covert signing, covert writing, covert typing) and, more generally, of motor imagery \citep{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018}.

One of the most influential theoretical model of this broad phenomenon, the motor simulation theory \cite{jeannerod_origin_2006, jeannerod_representing_1994, jeannerod_neural_2001}, contains the three following postulates: i) there exists a continuum between the covert (the mental representation) and the overt execution of an action, ii) action representations can operate off-line, via a simulation mechanism, and iii) covert actions rely on the same set of mechanisms as the overt actions they simulate, except that execution is inhibited (O’Shea \& Moran, 2017). A second class of explanatory models of motor imagery are concerned with the phenomenon of emulation and with internal models (see Gentsch et al., 2016, for a review of the similarities and dissimilarities between simulation and emulation models). Internal model theories share the postulate that action control uses internal models, that is, systems that simulate the behaviour of the motor apparatus (Jordan \& Rumelhart, 1992; Kawato et al., 1987). The function of internal models is to estimate and anticipate the outcome of a motor command. Among the internal model theories, motor control models based on robotic principles (e.g., Kawato, 1999; Wolpert et al., 1995) assume two kinds of internal models (that are supposed to be coupled and regulated): a forward model (or simulator) that predicts the sensory consequences of motor commands from efference copies of the issued motor commands, and an inverse model (or controller) that calculates the feedforward motor commands from the desired sensory states \cite{gentsch_towards_2016, loevenbruck_cognitive_2018}. Notice that in the following, we do not distinguish further between simulation and emulation, and we use these terms interchangeably to designate the mechanism through which sensory consequences of motor commands (or copy thereof) are computed by forward internal models...

% Because speech production results from sequences of motor commands which are assembled to reach a given communication goal, it belongs to the broader category of motor actions \citep{jeannerod_motor_2006}. Therefore, a parallel can be drawn between covert speech (also known as \textit{inner speech} or \textit{speech imagery}) and other forms of covert verbal actions (e.g., covert signing, covert writing, covert typing) and, more generally, of motor imagery \citep{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018}...

By building upon models of motor control (e.g., Houde \& Nagarajan, 2011; Wolpert et al., 1995), a recent model describes wilful (voluntary) expanded covert speech as "multi-modal acts with multi-sensory percepts stemming from coarse multi-sensory goals" (L\oe venbruck et al., 2018). In other words, this model considers the auditory and kinaesthetic sensations perceived during covert speech to be the predicted sensory consequences of inhibited speech motor acts, emulated by internal forward models that use the efference copies issued from an inverse model (this proposal shares some similarities with the emulation model of motor imagery, Grush, 2004). This model is supported by several empirical results providing both behavioural and neurophysiological evidence for the efference copies issued during inner speech production (e.g., Scott, 2013; Whitford et al., 2017)...

In this perspective, we explore some theoretical and experimental consequences of considering covert verbal actions (e.g., covert speech, covert typing) as inhibited verbal actions. We explore two main themes. First, we discuss the plausible origins of the sensory (e.g., auditory, tactile) content of covert verbal actions. Second, we discuss the under-explored role of inhibitory mechanisms during motor imagery and covert verbal actions. By bridging together recent results from motor imagery, motor inhibition, and inner speech research, we highlight some novel and possibly fruitful lines of research.

@@

\subsection{Sensory content: prediction-by-simulation vs. prediction-by-association}

Where does this sensory (e.g., auditory) content dome from? Prediction-by-simulation or prediction-by-association \citep{pickering_integrated_2013}? Direct simulation (attention-guided memory retrieval process) or indirect simulation (motor simulation process) \citep{tian_mental_2012, tian_effect_2013, li_corollary_2020, ma_distinct_2019}?

The balance between these two mechanisms may depend by the precise instructions given to the participants (see Figure \ref{fig:1} for a summary). More precisely, depending on whether they are instructed to "imagine speaking" or "imagine hearing" speech (similar to the distinction between the "inner ear" and the "inner voice", e.g., \cite{smith_subvocalization_1992})... distinct MEG correlates and effects on a subsequent categorisation task \citep{ma_distinct_2019}...

In the absence of non-ambiguous instructions, and in line with \cite{tian_mental_2012}, we suggest that the balance between these two mechanisms may depend on situational (e.g., surrounding noise) and intrinsic (e.g., expertise) characteristics. In addition to \cite{tian_mental_2012}, we suggest that a common currency determining the use of one of these mechanisms is the computational cost/resource, concept of memoisation \citep{dasgupta_memory_2021}... In other words, situational (extrinsic) and individual (intrinsic) characteristics jointly determine the computational cost (or equivalently, the available computational resources), which in turn determines the balance between the simulation and association mechanisms. Novel and/or difficult tasks may rely more on the simulation mechanism whereas well known tasks may rely more on associative mechanisms... See also the discussion in  \citep{nalborczyk_understanding_2019-1, nalborczyk_re-analysing_2020}...

\subsection{Development and novel actions}

How can we imagined totally novel (i.e., never executed) actions? The simulationnist framework suggests that multisensory percepts experienced during motor imagery would result from the simulation of the corresponding motor action, reusing internal models developed for the control of overt actions. In other words, internal models developed for the control of actions would then be used to simulate the sensory consequences of covert actions. Notice that these internal models are generative models, which means that they can a priori be used to compute (predict) the sensory consequences of any action that can be parsed as a (possibly supramodal) goal to an inverse internal model. In other words, although never formally tested, this framework entails that novel actions could be simulated internally.\footnote{Briefly mention the study by \cite{mulder_role_2004}...}

A prediction of this putative mechanism is that the imagination of novel actions (rather, the predicted sensory consequences of novel actions) may be "biased" (or "constrained") by the repertoire of already-known actions, given that internal models were developed based on precisely the repertoire of already-known actions. This prediction could be assessed by asking participants to imagine a novel action and subsequently checking whether this improves the execution of an intermediate (interpolated) novel action in the articulatory space. The same logic could be applied to the covert production of speech with someone else’s voice. How can we imagine speaking with the voice of our partner? If it is based on simulators (i.e., on internal models), then the covert production of speech with someone else’s voice should have sensory properties that are somehow “biased” or “constrained” by the properties of our own sensory and motor systems. Taking as an illustration the auditory sensations of speech, the subjective auditory sensation of covert speech with someone else’s voice should be situated in a somehow intermediate location in the auditory (e.g., formantic) space between the acoustic properties of our own voice and the acoustic properties of someone else voice.

This prediction could be assessed experimentally by...

@@

The proposal that overt and covert actions share common/similar neural circuits is faced with a serious problem. If the neural circuits used for the control of overt actions are reused for covert actions, how can covert actions not lead to execution? This puzzle, coined as \textit{the problem of inhibition} by \cite{jeannerod_neural_2001}, can be rephrased as follows: given the putative role of the motor system in providing the multisensory perceptual content of motor imagery, how is it possible for motor imagery not to lead to motor execution? In the following, we briefly summarise the evidence in favour of the view of covert verbal actions as inhibited verbal actions. Then, we discuss the relations between this view and the supposed progressive internalisation of speech in childhood. Finally, we outline some working hypotheses regarding the cognitive and neural implementation of these inhibitory mechanisms and their plausible roles in psychological disorders.

\subsection{Motor imagery as inhibited execution}

% In other words, despite the involvement of the motor system in providing the sensory experience of the covert action, how can we imagine raising our arm without actually raising our arm?

@@

More detailed categorisation of inhibitory mechanisms can occur at any location in this three-dimensional space but for the current purpose it is sufficient to say that we are interested (purportedly) in an intentional (we know we want to produce motor imagery rather than overt execution) but automatic (we do not explicitly think about not producing movements), planned ahead (proactive), and possibly global form of response inhibition... or maybe both global and effector-specifi, cf. the results of \cite{rieger_inhibition_2017}...

Inhibitory mechanisms underlying the ability to imagine actions \citep{guillot_imagining_2012, schwoebel_man_2002}. Neural correlates... the inhibitory triangle (cf. Figure \ref{fig:2}), composed of the preSMA, the rIFC, and the STN... A functional dissociation between the preSMA and the rIFC \citep{diesburg_pause-then-cancel_2021}... Moreover, they also reported a reduced short-interval intracortical inhibition (SICI) in patients with TS, a phenomenon that has been shown to be involved in response inhibition during motor imagery \citep{neige_unravelling_2020}...

\subsection{Learning not to produce speech}

\cite{watson_psychology_1919} suggested that thought (i.e., covert speech, in his terminology) was rooted in (overt) speech, that is, that it matured from overt speech... \cite{vygotsky_thought_1934} idea of speech internalisation and development of inhibition... Vygotsky observed, as Piaget did before, that egocentric or "private" speech tend to be internalised during child development... \cite{fernyhough_alien_2004} extended this model... What if speech internalisation was related to the development of inhibitory abilities?

These ideas could be assessed experimentally in several ways. First, the relation between speech internalisation and inhibitory abilities could be assessed during development at the critical ages (i.e., between 6 and 8 years). We would expect the ability to imagine actions and speech specifically to be positively correlated with inhibitory skills at at this stage...  \cite{wang_relationship_2021} provided correlational evidence that motor imagery and motor inhibition performance improve together between 7 and 11 years old, and that these two abilities correlated at 7 years old, but not later... Second, the inhibitory perspective presented here could be causally assessed by manipulation the inhibitory network preventing execution during motor imagery. For instance, using TMS, can we brake these inhibitory mechanisms and "force" execution during motor imagery... \citep{angelini_motor_2015, angelini_proactive_2016}... Third and finally, inhibition "deficits" in Tourette syndrom...

@@

We suggested that (section 1 propositions)... and (section 2 propositions)... Taken together, these propositions pave the way for many lines of research that should...

@@

@@

@@

@@

\begin{figure}[ht] % float was h! initially
\begin{center}
\includegraphics[width=0.75\textwidth]{figures/simulation_association.png} % This is a *.eps file
\end{center}
\caption{High-level depiction of the prediction-by-simulation (in blue) and prediction-by-association (in orange) mechanisms. The balance (weighting) between these two mechanisms during covert verbal actions depends on both task demands and "computational cost" (cf. text for more details), which are jointly determined by internal (individual) and external (situational) characteristics (e.g., expertise or (equivalently) task difficulty, noise, feedback perturbation).}\label{fig:1}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Succinct introduction in four paragraphs.
% ------------------------------------------
% 1) Introduction of motor imagery
% 2) Covert verbals actions
% 3) Relating 1) and 2) to the thematic of the research topic
% 4) Aims of the present perspective
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The ability to mentally examine our thoughts is central to our subjective experience. Mentally anticipating or rehearsing (verbal) actions allows us to become better at performing them \citep[e.g.,][]{toth2020}, to explore novel situations \citep{babar}, or to ... \citep{babar}. Broadly construed, motor imagery can be defined as the mental process by which one rehearses an action without engaging in the physical movements involved in this particular action. Because speech production results from sequences of motor commands that are assembled to reach a given communication goal, it belongs to the broader category of motor actions \citep{jeannerod_motor_2006}. Therefore, a parallel can be drawn between covert speech (also known as \textit{inner speech} or \textit{speech imagery}) and other forms of covert verbal actions (e.g., covert signing, covert writing, covert typing) and, more generally, of motor imagery \citep{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018}.

One of the most influential theoretical model of motor imagery the motor simulation theory \cite{jeannerod_origin_2006, jeannerod_representing_1994, jeannerod_neural_2001}, postulates the existence of a continuum between the covert and the overt execution of an action and that action representations can operate off-line via a simulation mechanism. In short, covert actions would rely on the same set of mechanisms as the overt actions they simulate, except that execution is inhibited \citep{oshea_does_2017}. A second class of models are concerned with the phenomenon of emulation \citep{grush_emulation_2004} and with internal models \cite[for a review of the similarities and dissimilarities between simulation and emulation models, see][]{gentsch_towards_2016}. Internal model theories share the postulate that action control uses internal models, that is, systems that simulate the behaviour of the motor apparatus \citep[e.g.,][]{jordan_forward_1992, kawato_hierarchical_1987}. The function of internal models is to estimate and anticipate the outcome of a motor command. Among the internal model theories, motor control models based on robotic principles \citep[e.g.,][]{kawato_internal_1999, wolpert_internal_1995} assume two kinds of internal models: a forward model (or simulator) that predicts the sensory consequences of motor commands from efference copies of the issued motor commands, and an inverse model (or controller) that calculates the feedforward motor commands from the desired sensory states \citep{gentsch_towards_2016, loevenbruck_cognitive_2018}. Notice that in the following, we do not distinguish further between simulation and emulation, and we use these terms interchangeably to designate the mechanism through which sensory consequences of motor commands (or copy thereof) are computed by forward internal models.

% By building upon models of speech motor control (e.g., Houde \& Nagarajan, 2011; Wolpert et al., 1995), a recent model describes wilful (voluntary) expanded covert speech as "multi-modal acts with multi-sensory percepts stemming from coarse multi-sensory goals" \cite{loevenbruck_cognitive_2018}. In other words, this model considers the auditory and kinaesthetic sensations perceived during covert speech to be the predicted sensory consequences of inhibited speech motor acts, emulated by internal forward models that use the efference copies issued from an inverse model (this proposal shares some similarities with the emulation model of motor imagery, Grush, 2004) \cite{grush_emulation_2004}. This model is supported by several empirical results providing both behavioural and neurophysiological evidence for the efference copies issued during inner speech production (e.g., Scott, 2013; Whitford et al., 2017)...

In this perspective, we explore some theoretical and experimental consequences of considering covert verbal actions (e.g., covert speech, covert typing) as inhibited verbal actions. We explore two main themes. First, we discuss the plausible origins of the multisensory (e.g., auditory, kinaesthetic) content of covert verbal actions. Second, we discuss the under-explored role of inhibitory mechanisms during motor imagery and covert verbal actions more specifically. By bridging together recent results from motor imagery, motor inhibition, and inner speech research, we highlight some novel and possibly fruitful lines of research.

@@

\subsection{Where does this sensory content come from?}

The production of covert speech is often accompanied by the feeling of hearing speech. In this section, we discuss a theoretical account of the mechanisms leading to the generation of these percepts during covert speech, while noticing that these mechanisms could be extended to other forms of covert verbal actions as well.

Where does this sensory (e.g., auditory) content dome from? Prediction-by-simulation or prediction-by-association \citep{pickering_integrated_2013}? Direct simulation (attention-guided memory retrieval process) or indirect simulation (motor simulation process) \citep{tian_mental_2012, tian_effect_2013, li_corollary_2020, ma_distinct_2019}? The dual stream prediction model \citep{tian_mental_2016}...

The balance between these two mechanisms may depend by the precise instructions given to the participants... More precisely, depending on whether they are instructed to "imagine speaking" or "imagine hearing" speech (similar to the distinction between the "inner ear" and the "inner voice", e.g., \cite{smith_subvocalization_1992})... distinct MEG correlates and effects on a subsequent categorisation task \citep{ma_distinct_2019}...

Memoisation: avoid redundant computation by storing computational results and reusing them later... functions call are intercepted with by a memoiser the inspects the previous calls of a function and its outputs. If a function has already been called with the same input, then the previously computed output is retrieved and reused... memoisation can be made more flexible (generalisable) by using \textit{interpolation} between cached outputs... for instance, in the context of motor control, reaching a goal (e.g., a cup of tea) can be decomposed in motor primitives, where input-output mapping can be retrieved from a memo table and/or interpolated from sufficiently similar stored mappings... or as put by \cite{dasgupta_memory_2021}, the "shift from algorithm to memory"... this shift is consistent with studies showing a lesser involvement of the motor system for well known imagined actions... Depending on whether the task needs to form "precise" sensory representations and whether we have the time resources to do it... training studies also suggest that we rely more and more on domain-general memory-processed with expertise \cite{tarr_mental_1989, jolicoeur_time_1985}...

In the absence of non-ambiguous instructions, and in line with \cite{tian_mental_2012}, we suggest that the balance between these two mechanisms may depend on situational (e.g., surrounding noise) and intrinsic (e.g., expertise) characteristics. In addition to \cite{tian_mental_2012}, we suggest that a common currency determining the use of one of these mechanisms is the computational cost/resource of either alternative. To clarify, we ... the concept of memoisation as applied to cognition and mental imagery \citep{dasgupta_memory_2021}. In this context, memory can be considered as a mechanisms to facilitate computational reuse. In the same way... efficient cognition may relies on stored past computation results rather than reinventing the wheel every time. In the context of motor and speech imagery... In other words, situational (extrinsic) and individual (intrinsic) characteristics jointly determine the computational cost (or equivalently, the available computational resources), which in turn determines the balance between the simulation and association mechanisms. Novel and/or difficult tasks may rely more on the simulation mechanism whereas well known tasks may rely more on associative mechanisms... See also the discussion in \citep{nalborczyk_understanding_2019-1, nalborczyk_re-analysing_2020}.

\subsection{The motor imagery of novel actions}

How can we imagine totally novel (i.e., never executed) actions? Broadly speaking, the simulationnist framework suggests that the multisensory experience of motor imagery would result from the simulation of the corresponding motor action, reusing internal models developed for the control of overt actions. In other words, internal models developed for the control of actions would then be used to simulate the sensory consequences of covert actions. Notice that these internal models are generative models, which means that they can a priori be used to compute (predict) the sensory consequences of any action that can be parsed as a (possibly supramodal) goal to an inverse internal model. In other words, this framework makes it possible for novel actions to be simulated internally.\footnote{\cite{mulder_role_2004} assessed whether the mental practice of a totally novel movement (abduction of the big toe of the dominant right foot) resulted in better overt execution over the course of several weeks of practice. They observed that although mental practise did improve execution in the group of participants that already had some experience with the task at baseline, mental practise did not lead to statistically significant improvements in execution in the group of participants that had zero experience with the task at baseline. However, a Bayesian reanalysis of their results suggests that the evidence in favour of the null hypothesis was rather inconclusive ($\text{BF}_{01} = 1.92$, using a weakly informative Cauchy prior on the standardised effect size for the alternative hypothesis, with $r = 1$).}

A prediction of this putative mechanism is that the imagination of novel actions, and more precisely, the predicted sensory consequences of novel actions, may be "biased" or "constrained" by the repertoire of already-known actions, given that internal models were developed based on precisely the repertoire of already-known actions. This prediction could be assessed by asking participants to imagine a novel action and subsequently checking whether this improves the execution of an intermediate (interpolated) novel action in the articulatory space. The same logic could be applied to the covert production of speech with someone else’s voice. How can we imagine speaking with the voice of our relatives? If it is based on simulators (i.e., on internal models), then the covert production of speech with someone else’s voice should possess sensory properties that are somehow "biased" or "constrained" by the properties of our own sensory and motor systems. Taking as an illustration the auditory sensations of speech, the subjective auditory sensation of covert speech with someone else’s voice should be situated in a somehow intermediate location in the auditory (e.g., formantic) space between the acoustic properties of our own voice and the acoustic properties of someone else voice.

This prediction could be assessed experimentally by... the prediction-by-simulation and the prediction-by-association accounts could be distinguished by constraining the motor system and assessing whether this influences the internal sensory representation of the produced speech. If it does...

@@

The proposal that overt and covert actions share common neural circuits is faced with a serious problem. If the neural circuits used for the control of overt actions are reused for covert actions, how can covert actions not lead to execution? This puzzle, coined as \textit{the problem of inhibition} by \cite{jeannerod_neural_2001}, can be rephrased as follows: given the putative role of the motor system in providing the multisensory content of motor imagery, how is it possible for motor imagery not to lead to motor execution? In the following, we briefly summarise the evidence in favour of the view of covert verbal actions as inhibited verbal actions. Then, we discuss the relations between this view and the presumed progressive internalisation of speech during childhood. Finally, we outline some working hypotheses regarding the cognitive and neural implementation of these inhibitory mechanisms \textit{(and their plausible roles in psychological disorders)}.

\subsection{Cognitive mechanisms and neural implementation}

@@

More detailed categorisation of inhibitory mechanisms can occur at any location in this three-dimensional space but for the current purpose it is sufficient to say that we are interested (purportedly) in an intentional (we know we want to produce motor imagery rather than overt execution) but automatic (we do not explicitly think about not producing movements), planned ahead (proactive), and possibly global form of response inhibition... or maybe both global and effector-specific, cf. the results of \cite{rieger_inhibition_2017}...

Inhibitory mechanisms underlying the ability to imagine actions \citep{guillot_imagining_2012, schwoebel_man_2002}... mentioning the success of BCI with neural activity recorded in premotor/motor areas durmong motor imagery and silent speech... Neural correlates... the inhibitory triangle (cf. Figure \ref{fig:2}), composed of the preSMA, the rIFC, and the STN... A functional dissociation between the preSMA and the rIFC \citep{diesburg_pause-then-cancel_2021}... Moreover, they also reported a reduced short-interval intracortical inhibition (SICI) in patients with TS, a phenomenon that has been shown to be involved in response inhibition during motor imagery \citep{neige_unravelling_2020}...

Inhibition or subliminal activity/bypassing? \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016} vs. \cite{loevenbruck_cognitive_2018}... However, stating that motor imagery only involve subthreshold activity (and therefore is not accompanied by the emission of motor commands that to be inhibited) simply shifts the problem from "how and where motor commands are subsequently inhibited" to "how and where the magnitude of activity in the motor system is planned". In other words, we still need to explain how (in a mechanistic and/or developmental way) this activity is maintained at a subthreshold level. What cognitive and neural mechanisms operate in order to maintain this activity under the threshold? In this section, we provided empirical arguments in favour of the first "active inhibition hypothesis", but proponents of the "subliminal hypothesis" need to clarify how this activity is maintained at a subthreshold level during motor imagery, thus preventing execution.

\subsection{Inner speech development: Learning not to produce speech}

\cite{watson_psychology_1919} suggested that thought (i.e., covert speech, in his terminology) was rooted in (overt) speech, that is, covert speech matured from overt speech. \cite{vygotsky_thought_1934} then prominently formulated the that inner speech originates in overt speech, and more specifically, in private egocentric speech, that is, self-addressed overt speech in childhood. The idea of speech internalisation and development of inhibition... Vygotsky observed, as Piaget did before, that egocentric or "private" speech tend to be internalised during child development... \cite{fernyhough_alien_2004} extended this model... What if speech internalisation was related to the development of inhibitory abilities?

These ideas could be assessed experimentally in several ways. First, the relation between speech internalisation and inhibitory abilities could be assessed during development at the critical ages (i.e., between 6 and 8 years). We would expect the ability to imagine actions and speech specifically to be positively correlated with inhibitory skills at at this stage...  \cite{wang_relationship_2021} provided correlational evidence that motor imagery and motor inhibition performance improve together between 7 and 11 years old, and that these two abilities correlated at 7 years old (but did not correlate at 11 years old). Second, the inhibitory perspective presented here could be causally assessed by manipulation the inhibitory network preventing execution during motor imagery. For instance, using TMS, can we brake these inhibitory mechanisms and "force" execution during motor imagery... \citep{angelini_motor_2015, angelini_proactive_2016}... Third and finally, inhibition "deficits" in Tourette syndrom...

@@

We suggested that (section 1 propositions)... and (section 2 propositions)... Taken together, these propositions pave the way for several lines of research that should...

@@

\color{blue}

@@

\color{black}

@@

None.

@@

% \begin{figure}[ht] % float was h! initially
% \begin{center}
% \includegraphics[width=0.75\textwidth]{figures/simulation_association.png} % This is a *.eps file
% \end{center}
% \caption{High-level depiction of the prediction-by-simulation (in blue) and prediction-by-association (in orange) mechanisms. The balance (weighting) between these two mechanisms during covert verbal actions depends on both task demands and "computational cost" (cf. text for more details), which are jointly determined by internal (individual) and external (situational) characteristics (e.g., expertise or (equivalently) task difficulty, noise, feedback perturbation).}\label{fig:1}
% \end{figure}
